Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-05-09 icdm/submission/includes/related_work.tex
shenanigans intel

\subsection{Parallization in shared and Distributed Memory}
In contrast to the above approach, this one, introduced by Ji et al. \cite{intel} focused on the SGNS. The focus of this work was to speed up the computation of the loss function of the SGNS described in Equation \ref{eq:obj_neg_samples}. Where the dot product of the center word  with negative samples as well as the context word is computed. The dot product is a level 1-BLAS operation and is not as efficiently implemented into hardware, as matrix multiplication which are a level 3-BLAS operation.  To achieve such a transformation, Ji et al. decided to use the same negative samples for given amount of training samples. The training samples that will have the same negative samples are chosen as follows: given a word $w_c$ one can construct all the training samples where $w_c$ is a context word. This will result in the following training batch $X = \{({w_{in}}^i, w_c) | w_c~appears~in~the~context~of~{w_{in}}^i\}$. The matrix multiplication can be represented in the following way.
\[
\begin{bmatrix}
w_c \\
w_{n_1} \\
\vdots \\
w_{n_k}\\
\end{bmatrix}
*
\begin{bmatrix}
w_{in}^1\\
\vdots\\
{w_{in}}^{2m}\\
\end{bmatrix}
\]
where, $w_{n_1}...w_{n_k}$ are the shared negative samples. The above Matrix multiplication will compute the loss for each training sample and the weights of the used vectors will be updated after each batch. This method achieves a 3.6 fold increase in throughput, by only losing 1\% of accuracy. The presented results were achieved on CPU's, as many modern machine learning libraries make use of the parallelizing capabilities of GPU's for matrix multiplications, the next subsection covers the work done by Seulki and Youngmin \cite{gpu} that parellelized the SGNS on GPU's.

>>>>

\subsection{Parallization in shared and Distributed Memory}
In contrast to the above approach, this one, introduced by Ji et al. \cite{intel} focused on the SGNS. The focus of this work was to speed up the computation of the loss function of the SGNS described in Equation \ref{eq:obj_neg_samples}. Where the dot product of the center word  with negative samples as well as the context word is computed. The dot product is a level 1-BLAS operation and is not as efficiently implemented into hardware, as matrix multiplication which are a level 3-BLAS operation.  To achieve such a transformation, Ji et al. decided to use the same negative samples for given amount of training samples. The training samples that will have the same negative samples are chosen as follows: given a word $w_c$ one can construct all the training samples where $w_c$ is a context word. The following training batch $X$ will result: $X = \{({w_{in}}^i, w_c) | w_c~appears~in~the~context~of~{w_{in}}^i\}$. The matrix multiplication can be represented in the following way:
\[
\begin{bmatrix}
w_c \\
w_{n_1} \\
\vdots \\
w_{n_k}\\
\end{bmatrix}
*
\begin{bmatrix}
w_{in}^1\\
\vdots\\
{w_{in}}^{2m}\\
\end{bmatrix}
\]
where, $w_{n_1}...w_{n_k}$ are the shared negative samples. The above Matrix multiplication will compute the loss for each training sample and the weights of the used vectors will be updated after each batch. Ji et al.'s method achieves a 3.6 fold increase in throughput, by only losing 1\% of accuracy. The presented results were achieved on CPU's, as many modern machine learning libraries make use of the parallelizing capabilities of GPU's for matrix multiplications, the next subsection covers the work done by Seulki and Youngmin \cite{gpu} that parellelized the SGNS on GPU's.
